### 2018-11-29 manuscript/manuscript.rmd
updated R code for new paths, now parse partition clusters

papers = read_tsv( "tables/papers.tsv" )
datasets = read_tsv( "tables/datasets.tsv" )
analyses = 
	read_tsv( "tables/analyses.tsv", col_types = 'iccccccccccclnnnncc' ) %>%
	mutate( taxon_sampling = factor( taxon_sampling, levels= c( 'Choanimalia', 'Holozoa', 'Opisthokonta' ) ) )

@@

taxa = 
	read_tsv("taxonomy_info/taxon_table.tsv") %>% 
	distinct( relabelled_name, clade_assignment, ncbi_tax_id ) %>%
	dplyr::rename( taxon=relabelled_name, clade=clade_assignment ) %>%
	mutate( clade = factor( clade, levels=clades )  )

@@

a_file = "blast/phylips/Chang2015_Chang2015.phy"
p_file = "blast/phylips/Chang2015_Chang2015.nex"
msa = PartitionedMultipleAlignment( a_file, p_file, taxa )

@@

partition_clusters = 
	read_tsv( "blast/graphs/diamond_partition_clusters.tsv" ) %>% 
	dplyr::rename( partition=partition_name ) %>%
	dplyr::rename( matrix=dataset ) %>%
	dplyr::rename( cluster_id=cluster_number )

busco_results = 
	read_tsv("blast/graphs/busco_metazoa_results.tsv") %>% 
	filter( Status != "Missing" )

sequences_all_txt = 
	read_tsv("blast/all_parts_list.txt")

@@

analyses %>% 
	ggplot( aes(x=model_summary, y=taxon_sampling, col=result) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()
```

@@

Dtaxaxman = 
	read_tsv("~/Dropbox/repo/animal_root/blast/graphs/cross_mscript_taxa.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

@@

Dtaxa = 
	read_tsv("~/Dropbox/repo/animal_root/blast/graphs/taxon_graph.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

@@

taxonomy_reference = read_tsv("taxonomy_info/taxon_table.tsv")

>>>>

papers = read_tsv( "../data_processed/tables/previously_published_manuscripts.tsv" )
datasets = read_tsv( "../data_processed/tables/previously_published_datasets.tsv" )
analyses = 
	read_tsv( "../data_processed/tables/previously_published_analyses.tsv", col_types = 'iccccccccccclnnnncc' ) %>%
	mutate( clade = factor( clade, levels= c( 'Choanimalia', 'Holozoa', 'Opisthokonta' ) ) )

taxonomy_reference = read_tsv("../reconciliation/taxonomy_info/taxon_table.tsv")

partition_map_global = 
	read_tsv("../reconciliation/blast/graphs/diamond_partition_clusters.tsv") %>%
	dplyr::rename(partition=partition_name) %>%
	dplyr::rename(matrix=dataset)

@@

taxa = 
	taxonomy_reference %>% 
	distinct( relabelled_name, clade_assignment, ncbi_tax_id ) %>%
	dplyr::rename( taxon=relabelled_name, clade=clade_assignment ) %>%
	mutate( clade = factor( clade, levels=clades )  )

@@

a_file = "../data_processed/matrices/Chang2015_Chang2015.phy"
p_file = "../data_processed/matrices/Chang2015_Chang2015.nex"
msa = PartitionedMultipleAlignment( a_file, p_file, taxa, partition_map_global=partition_map_global, manuscript_name="Chang2015", matrix_name="Chang2015")

@@

partition_clusters = 
	read_tsv( "../reconciliation/blast/graphs/diamond_partition_clusters.tsv" ) %>% 
	dplyr::rename( partition=partition_name ) %>%
	dplyr::rename( matrix=dataset ) %>%
	dplyr::rename( cluster_id=cluster_number )

busco_results = 
	read_tsv("../reconciliation/blast/graphs/busco_metazoa_results.tsv") %>% 
	filter( Status != "Missing" )

sequences_all_txt = 
	read_tsv("../reconciliation/blast/all_parts_list.txt")

@@

analyses %>% 
	ggplot( aes(x=model_summary, y=clade, col=result) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()
```

@@

Dtaxaxman = 
	read_tsv("../reconciliation/blast/graphs/cross_mscript_taxa.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

@@

Dtaxa = 
	read_tsv("../blast/graphs/taxon_graph.tsv") %>%
	arrange( mscript1, dataset1, taxon1, mscript2, dataset2, taxon2 )

@@
